Columnar VCF for Biobank scale datasets using Zarr

### 2024-04-09 paper.tex
Update whole matrix compute fig
Some text

\begin{figure}
\includegraphics[width=6cm]{figures/whole-matrix-compute}
\caption{Whole-matrix compute performance with increasing sample size.
Total CPU time required to run \texttt{bcftools +af-dist}
and equivalent operations in a single thread for various tools.
Elapsed time is also reported (dotted line). Run-time for genozip
at $10^6$ samples was extrapolated by fitting an exponential.
\label{fig-whole-matrix-compute}}
\end{figure}

Figure~\ref{fig-whole-matrix-compute} shows the results of 
running \texttt{bcftools +af-dist} and equivalent operations 
on the data of Figure~\ref{fig-data-storage}.

>>>>

\begin{figure}
\includegraphics{figures/whole-matrix-compute}
\caption{Whole-matrix compute performance with increasing sample size.
Total CPU time required to run \texttt{bcftools +af-dist}
and equivalent operations in a single thread for various tools.
Elapsed time is also reported (dotted line). Run-time for genozip
at $10^6$ samples was extrapolated by fitting an exponential.
\label{fig-whole-matrix-compute}}
\end{figure}

Figure~\ref{fig-whole-matrix-compute} shows the results of 
running \texttt{bcftools +af-dist} and equivalent operations 
on the data of Figure~\ref{fig-data-storage}. We can see 
that for $10^6$ samples, running \texttt{bcftools +af-dist}
requires 20 hours (note that this is run on a BCF file, for 
efficiency), which can be regarded as a reasonable baseline.
Because genozip does not provide an API, we used the classical
approach of piping the VCF text that it outputs into 
\texttt{bcftools +af-dist}. The volumes of data involved here
make this an expensive approach.
[TODO discuss Zarr-python and Savvy C++ implementations]
